Disparity through time - for appendix

### 2018-02-05 analyses/10-appendix-figure-dtt.Rmd
Add edits to epoch appendix figure

pdf("../manuscript/figures/fig-dtt-age-appendix.pdf")  
  multiplot(beck_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            brusatte_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            wright_s + theme(plot.margin=unit(c(5.5, 5.5, 12, 25),"points")), 
            beck_d, brusatte_d, bapst_d, 
            wright_d + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            beck_n,
            brusatte_n,
            bapst_n,
            wright_n + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            cols = 3, 
            labs = list("Time (MYA)", 
                        "Relative disparity"),
            labpos=list(c(0.5, 0.015), c(0.03, 0.5)))
dev.off()
```

@@

beck_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(100, 0),
                  breaks = c(seq(100, 0, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()
        )

beck_s <- 
  beck_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Stratigraphy") +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        legend.position = "none") +
  annotate("text", x = 75, y = 0.15, label = "Beck2014")

beck_d <- 
  beck_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Duration") +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        legend.position = "none")

beck_n <- 
  beck_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Number") +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        legend.key.size = unit(0.2, "in"),
        legend.text = element_text(size = 8),
        legend.title=element_blank())

@@

brusatte_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(170, 70),
                  breaks = c(seq(170, 70, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

brusatte_s <- 
  brusatte_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  annotate("text", x = 140, y = 0.15, label = "Brusatte2014")

brusatte_d <- 
  brusatte_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8)

brusatte_n <- 
  brusatte_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8)

@@

```{r}
bapst_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(200, 50),
                  breaks = c(seq(200, 50, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

bapst_s <- 
  bapst_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  annotate("text", x = 165, y = 0.15, label = "Bapst2016")

bapst_d <- 
  bapst_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8)

bapst_n <- 
  bapst_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8)

@@

wright_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(470, 370),
                  breaks = c(seq(470, 370, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

wright_s <- 
  wright_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  annotate("text", x = 440, y = 0.15, label = "Wright2017")

wright_d <- 
  wright_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  scale_x_reverse(limits = c(470, 370),
                  breaks = c(seq(470, 370, by = -100)))

wright_n <- 
  wright_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8)

@@

pdf("../manuscript/figures/fig-dtt-epoch-appendix.pdf")  
  multiplot(beck_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            brusatte_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            wright_s + theme(plot.margin=unit(c(5.5, 5.5, 12, 25),"points")), 
            beck_d, brusatte_d, bapst_d, 
            wright_d + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            beck_n,
            brusatte_n,
            bapst_n,
            wright_n + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            cols = 3, 
            labs = list("Time (MYA)", 
                        "Relative disparity"),
            labpos=list(c(0.5, 0.015), c(0.03, 0.5)))
dev.off()
```

>>>>

pdf("../manuscript/figures/fig-dtt-age-appendix-revision.pdf")  
  multiplot(beck_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            brusatte_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            wright_s + theme(plot.margin=unit(c(5.5, 5.5, 12, 25),"points")), 
            beck_d, brusatte_d, bapst_d, 
            wright_d + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            beck_n,
            brusatte_n,
            bapst_n,
            wright_n + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            cols = 3, 
            labs = list("Time (MYA)", 
                        "Relative disparity"),
            labpos=list(c(0.5, 0.015), c(0.03, 0.5)))
dev.off()
```

@@

beck_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(100, 0),
                  breaks = c(seq(100, 0, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()
        ) +
  scale_colour_viridis(discrete = TRUE, direction = -1, end = 0.8)

@@

@@

bapst_s <- 
  bapst_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3) +
  annotate("text", x = 165, y = 0.15, label = "Bapst2016")

bapst_d <- 
  bapst_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 3, alpha = 0.3)

@@

@@

pdf("../manuscript/figures/fig-dtt-epoch-appendix-revision.pdf")  
  multiplot(beck_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            brusatte_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            wright_s + theme(plot.margin=unit(c(5.5, 5.5, 12, 25),"points")), 
            beck_d, brusatte_d, bapst_d, 
            wright_d + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            beck_n,
            brusatte_n,
            bapst_n,
            wright_n + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            cols = 3, 
            labs = list("Time (MYA)", 
                        "Relative disparity"),
            labpos=list(c(0.5, 0.015), c(0.03, 0.5)))
dev.off()
```
